---
title: "Summary report - AFSC Age and Growth Progam data"
format: html
editor: visual
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup}

source("Code/age_demo_main.R") #main script
knitr::opts_chunk$set(fig.pos = "H", out.extra = "") #prevent figures from floating

```

# [COLLECTION: **`r collection.name`**]{.underline}

## AGE AGREEMENT - TRADITIONAL AGE READING

The information below describes results of paired age readings between a primary age reader ("Read age") and a second reader ("Test age"). Generally, the AFSC Age and Growth Program performs paired readings on 20% of each collection. These paired test and read age estimates are used to evaluate inter-reader precision and bias. Acceptable levels of precision vary among species. Precision statistics are compared to those of previous collections, and if they fall well outside of the norm, specimens may be re-aged or a larger portion of the cruise may be tested by the second reader. In cases where bias is detected between reader and tester, they work together to identify the source of the bias and resolve "Final Ages" prior to releasing data to the user.

| **Precision statistic**                     | **Value**                                              |
|---------------------------------------|---------------------------------|
| Percent agreement (PA)                      | `r round(precision$PercAgree, 2)`%                     |
| Average percent error (APE)                 | `r round(precision$APE, 2)`%                           |
| Coefficient of variation (CV)               | `r round(precision$ACV, 2)`%                           |
| Total number of fish in ageing collection   | `r nrow(data)`                                         |
| Number of fish unaged                       | `r nrow(data[is.na(data$final_age),])`                 |
| Number of fish in precision-testing sample  | `r precision$n`                                        |
| Number of fish aged by two readers          | `r precision$validn`                                   |
| Percentage of fish with paired age readings | `r round(precision$validn/nrow(data)*100,0)`           |
| Average read age (paired reads only)        | `r round(mean(trad.testing$read_age, na.rm = TRUE),2)` |
| Average test age (paired reads only)        | `r round(mean(trad.testing$test_age, na.rm = TRUE),2)` |

: Precision statistics for the `r collection.name` collection.

{{< pagebreak >}}

```{r}
#| echo: false
#| output: false

bowker <- summary(bias, what = "Bowker")
evanshoenig <- summary(bias, what = "EvansHoenig")
mcnemar <- summary(bias, what = "McNemar")

```

::: {#tbl-panel layout-ncol="1"}
|                    |                         |                     |
|--------------------|-------------------------|---------------------|
| minus bias         | `r minus.bias` otoliths | `r minus.bias.per`% |
| plus bias          | `r plus.bias` otoliths  | `r plus.bias.per`%  |
| complete agreement | `r agree` otoliths      | `r agree.per`%      |

: Bias direction {#tbl-first}

\

| **Test name** | **df**                | **Test statistic**                 | ***p***                       |
|------------------|------------------|------------------|------------------|
| Bowker's      | `r bowker["df"]`      | `r round(bowker["chi.sq"],2)`      | `r round(bowker["p"],2)`      |
| Evans-Hoenig  | `r evanshoenig["df"]` | `r round(evanshoenig["chi.sq"],2)` | `r round(evanshoenig["p"],2)` |
| McNemar       | `r mcnemar["df"]`     | `r round(mcnemar["chi.sq"],2)` |  `r round(mcnemar["p"],2)`        |

: Tests of symmetry {#tbl-second}

Bias statistics for the `r collection.name` collection. The null hypothesis of the tests is that there is no asymmetry among cells off the diagonal of a cross-tabulation table.
:::

```{r}
#| echo: false
#| output: false

cont.table <- summary(bias, what = "table")

cont.table[cont.table == 0] <- "-"

dimnames(cont.table)

```

```{r}
kableExtra::kable(cont.table, row.names = TRUE, 
                  caption = "Cross-tabulation showing Test Age (columns) vs Read Age (rows)")


```

{{< pagebreak >}}

\

```{r bias-plot}
#| fig-cap: Bubble plot comparing age estimates between reader and tester of this collection. The solid diagonal line represents a 1:1 relationship. The red dashed line represents a fitted generalized additive model.
#| fig-height: 6
#| 
bubble.diag 

```

```{r cv-by-age}
#| fig-cap: Mean CV by age group of this collection, with 95% confidence intervals. Red dashed line indicates overall mean CV for the collection.
#| fig-width: 6.5
#| 
cv.mean.age 

```

{{< pagebreak >}}

```{r hist-agree}
#| fig-cap: Comparison of reader agreement metrics between this collection (red point) and historical collections of the same species (gray points). Average test age versus percent agreement (top) and average CV (bottom). Dashed line and gray area indicate 95% and 99% confidence ellipses, respectively. Blue line indicates fitted generalized additive model. Points outside the ellipse but *above* the GAM in the case of percent agreement or *below* the GAM in the case of CV would still be desirable outcomes because they indicate better precision than expected for this species. Note that historical collections are summarized at the reader level, sometimes with multiple readers for a given year and cruise.
#| fig-width: 6.5
#| fig-height: 7
#| 
hist.compare 

```

{{< pagebreak >}}

## AGE RANGES

This section shows information pertaining to the full collection of `r unique(str_to_title(data$common_name))` aged from the `r unique(paste(data$collection_year, data$region, data$collection_type, sep=" "))`, including age and size distributions and length-at-age.

|                     |                                               |
|---------------------|-----------------------------------------------|
| Average age (years) | `r round(mean(data$final_age, na.rm=TRUE),2)` |
| Median age (years)  | `r median(data$final_age, na.rm=TRUE)`        |
| Average length (mm) | `r round(mean(data$length, na.rm=TRUE),0)`    |
| Median length (mm)  | `r median(data$length, na.rm=TRUE)`           |
| Average weight (g)  | `r round(mean(data$weight, na.rm=TRUE))`      |
| Median weight (g)   | `r median(data$weight, na.rm=TRUE)`           |

\

```{r weight-length}
#| fig-cap: Observations of weight-at-length for males, females, and unsexed individuals.
#| fig-width: 6.5
#| 
lw.plot

```

{{< pagebreak >}}

```{r age-length-dist}
#| fig-cap: Age (top) and length (bottom) distributions of fish aged by the AFSC Age and Growth Program. Dashed red line represents the mean, solid black line represents the median.
#| fig-height: 6
#| 
dist.plot

```

{{< pagebreak >}}

```{r vonB}
#| fig-cap: Observations of length (top) and weight (bottom) at age with fitted von Bertalanffy growth functions for males and females.
#| fig-width: 6.5
#| fig-height: 8
#| fig-pos: 'h'
#| 
vonBs

```
